A neural coarse graining theory of consciousness

### 2019-01-21 Paper_neural_coarse_graining_of_consciousness.tex
Updates from ShareLaTeX
20190121_151428

	% ============================================================================ %
	%                                  Out theory                                  %
	% ============================================================================ %
	\section{A neural coarse graining theory of consciousness}
		\ideaBox{Need to describe my intuition more concretely}

		\begin{ants}
			\toWrite{Do I need to start with my philosophical intuition?}

@@

		% ----------------------------------------------------------------------------

			%% reasoning

				@ ============= reasoning ============

@@

			%% our claim
				@ ============ our claim  ============

				@ We claim that the state of a coarse-grained scale which realises non-trivial informational closured correlates the state of consciousness.

@@

			%% Following
				@ In the following part, we....\todo{todo}

@@

				@@ Oppenheim , P. , \& Putnam , H. ( 1958 ). Unity of science as a working hypothesis . In H. Feigl , G. Maxwell , \& M. Scriven (Eds.), Concepts, theories, and the mind – body problem (pp. 3 – 36 ). Minneapolis : University of Minnesota Press .
				@@ Attneave , F. ( 1961 ). In defense of homunculi . In W. A. Rosenblith (Ed.), Sensory communication (pp. 777 – 782 ). Cambridge, MA : MIT Press .
				@@ Hofstadter , D. R. ( 1979 ). Godel, Escher, Bach, an eternal golden braid . New York : Basic Books .
				@@ Churchland , P. S. , \& Sejnowski , T. J. ( 1992 ). The computational brain . Cambridge, MA : MIT Press .
				@@ Wimsatt , W. C. ( 1994 ). The ontology of complex systems: levels of organization, perspectives, and causal thickets. Canadian Journal of Philosophy , 20 , 207 – 274 .
				@@ Lycan ,  W. G.  ( 1996 ).  Consciousness and experience .  Cambridge, MA :  MIT Press .

@@

		\subsection{Measure of conscious level}
			\begin{ants}
				@ The level of consciousness can be computed from how much degree of the non-trivial informational closure in a coarse-grained scale.

@@

		\subsection{Conscious contents}
			\begin{ants}
				@ We claim that conscious contents correspond to the state of the informational closure.

@@

>>>>

	\section{A neural coarse graining theory of consciousness}

	    \subsection{reasoning about this idea}
		\begin{ants}
	    % Intuition

@@

		% Reasoning

@@

        % our claim   
			@ We claim that the state of a coarse-grained scale which realises non-trivial informational closured correlates the state of consciousness.

@@

		% Following
			@ In the following part, we....\todo{todo}

@@

				@@ Oppenheim , P. , \& Putnam , H. ( 1958 ). Unity of science as a working hypothesis . In H. Feigl , G. Maxwell , \& M. Scriven (Eds.), Concepts, theories, and the mind – body problem (pp. 3 – 36 ). Minneapolis : University of Minnesota Press .
				@@ Attneave , F. ( 1961 ). In defense of homunculi . In W. A. Rosenblith (Ed.), Sensory communication (pp. 777 – 782 ). Cambridge, MA : MIT Press .
				@@ Hofstadter , D. R. ( 1979 ). Godel, Escher, Bach, an eternal golden braid . New York : Basic Books .
				@@ Churchland , P. S. , \& Sejnowski , T. J. ( 1992 ). The computational brain . Cambridge, MA : MIT Press .
				@@ Wimsatt , W. C. ( 1994 ). The ontology of complex systems: levels of organization, perspectives, and causal thickets. Canadian Journal of Philosophy , 20 , 207 – 274 .
				@@ Lycan ,  W. G.  ( 1996 ).  Consciousness and experience .  Cambridge, MA :  MIT Press

@@

		\subsection{Measure of consciousness/information correlate of consciousness}

			@ In this framework, we postulate that the NTIC process is the core entity of information correlate of consciousness.

			@ The content of consciousness corresponds to the state of the NTIC process.
				\begin{equation}\label{eq:cContent}
					C_{t}^{Content} = Y_{t}
				\end{equation}

			@ Furthermore, we can compute the level of consciousness via knowing the amount of information enclosed in a NTIC process.

			@ We postulate that levels of consciousness $C_{t}^{Level}$ corresponds to the degree of NTIC at the coarse-grained level $NTIC_{t}$ at time $t$.

				\begin{equation}\label{eq:cLevel}
					C_{t}^{Level} = NTIC_{t}
				\end{equation}

			@ Therefore, this framework well integrates the two key but debated concepts in consciousness research \citep{laureys2005neural, bayne2016there}.

			\subsubsection{consicous level}
			@ This implies that, based on the Equation \ref{eq:nticObjective}, the self-predictive information about the future states that the current state holds and the information about the environment encoded in the process determine the level of consciousness.

			@ This also suggests that the richness of the environment being modelled by the			NTIC process has a direct contribution to the level of consciousness.

@@

		\subsection{Coarse-graining states correlates conscious contents}
			\begin{ants}
				@ We claim that conscious contents correspond to the state of the informational closure.

@@

			@ This is similar to the the \textit{Information} axiom in integrated information theory which claims that

\textquote[\citep[p. 2]{oizumi2014phenomenology}]{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...}

``...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...''\citep[p. 2]{oizumi2014phenomenology}
